Microlensing as a possible probe of event-horizon structure in quasars

### 2016-03-14 paper1/ms.tex
typo fix

Section~\ref{sec:fold-crossing} shows the light curves that result
when each of the model sources crosses an ideal fold.  This would
apply in Figure~\ref{fig:magnification_map} to sources along the path
AB or BC, for sources small enough that the curvature of the caustics
is negligible.  With this assumption one can imagine the caustic as an
infinite wall to be crossed by the source as presented in
Figure~\ref{fig:infinite_fold}.  The source brightness distribution
parallel to the caustic naturally makes no difference to the
observable brightness; each source can be replaced by an effective
one-dimensional source profile, by flattening the source so it becomes
perpendicular to the caustic.  In principle, the effective
one-dimensional brightness profile could be recovered from the light
curve by deconvolution.  \cite{1999ApJ...524...49A} modelled this
profile as the result of a circular accretion disc seen through the
spacetime around a Kerr black hole, and \cite{2012MNRAS.423..676A}
have applied the idea to observed light curves to infer properties of
quasar accretion discs.  In this work we take a simpler but arguably
more robust approach: we study features in the light curves
characteristic of a crescent-like source which in turn would indicate
a black-hole silhouette.  Figure~\ref{fig:char_points} shows the
qualitative features: there is a period during which the dark cutout
disc is crossing the caustic, and before and after there are periods
when the only the bright parts of the crescent are in transit across
the caustic.  The details depend on the orientation of the crescent,
but basically the dark disc causes a rising light curve to plateau or
dip.  These features are still present, albeit faintly, if the simple
crescent is replaced by a source based on an accretion-disc simulation
of a black-hole environment
(Figures~\ref{fig:M87_plots}--\ref{fig:char_points}).

>>>>

Section~\ref{sec:fold-crossing} shows the light curves that result
when each of the model sources crosses an ideal fold.  This would
apply in Figure~\ref{fig:magnification_map} to sources along the path
AB or BC, for sources small enough that the curvature of the caustics
is negligible.  With this assumption one can imagine the caustic as an
infinite wall to be crossed by the source as presented in
Figure~\ref{fig:infinite_fold}.  The source brightness distribution
parallel to the caustic naturally makes no difference to the
observable brightness; each source can be replaced by an effective
one-dimensional source profile, by flattening the source so it becomes
perpendicular to the caustic.  In principle, the effective
one-dimensional brightness profile could be recovered from the light
curve by deconvolution.  \cite{1999ApJ...524...49A} modelled this
profile as the result of a circular accretion disc seen through the
spacetime around a Kerr black hole, and \cite{2012MNRAS.423..676A}
have applied the idea to observed light curves to infer properties of
quasar accretion discs.  In this work we take a simpler but arguably
more robust approach: we study features in the light curves
characteristic of a crescent-like source which in turn would indicate
a black-hole silhouette.  Figure~\ref{fig:char_points} shows the
qualitative features: there is a period during which the dark cutout
disc is crossing the caustic, and before and after there are periods
when the only the bright parts of the crescent are in transit across
the caustic.  The details depend on the orientation of the crescent,
but basically the dark disc causes a rising light curve to plateau or
dip.  These features are still present, albeit faintly, if the simple
crescent is replaced by a source based on an accretion-disc simulation
of a black-hole environment
(Figures~\ref{fig:M87_image}--\ref{fig:M87_plots}).
